Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-06 background.tex

It is recommended that for the load balance purpose, a proper dragonfly configuration should follow $a=2p=2h$~\cite{kim-micro}. According to this configuration, the total number of groups, denoted as $g$ in the dragonfly network would be $g = a*h+1 $, the total number of compute nodes denoted as $N$ in the network would be $N = p*a*g $. An implementation of dragonfly network follows such configuration is illustrated in Figure~\ref{fig:dragonfly-overview}. There are six routers in each group, each router has three compute nodes attached to it. This dragonfly network consists of 19 groups and 342 nodes in total.

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.48\textwidth]{dragonfly-overview}
  \caption{Dragonfly Network Overview. There are 19 groups, six routers in each group, three compute nodes connected to each router, 342 nodes in total. Job $J1$ requires seven nodes, getting its allocation by random placement. Job $J2$ requires eight nodes, getting its allocation by contiguous placement.}
  \label{fig:dragonfly-overview}
\end{figure}

@@

\textbf{Minimal:} In this policy, a message takes the shortest path from the source router to the destination router. When there are multiple shortest paths between the source and destination, the message will be evenly divided among the paths. Minimal routing can guarantee the minimum hops the message takes from the source to the destination. However, it may result in congestion along the shortest paths.

\textbf{Adaptive:} In this policy, the path a message takes will be adaptively chosen between shortest and non-shortest paths, depending on the congestion situation along those paths. For the non-shortest path, an intermediate router will be randomly chosen. The message takes the intermediate router as a via point, connecting the source and destination router through two separate shortest paths. Adaptive routing can avoid hot-spots in the presence of congestion and collapse to minimal routing otherwise.

\textbf{Progressive Adaptive:} In this policy, the decision to route minimally at each hop in the source group will be re-evaluated. Any decision to route non-minimally at source router or at a subsequent hop is permanent and will not be re-evaluated~\cite{jiang}. The progressive adaptive is capable of handling the case when a global channel is congested but the source router has not been informed yet~\cite{jiang}. The packet will take the non-minimal route only when the congestion is encountered.

>>>>

It is recommended that for the load balance purpose, a proper dragonfly configuration should follow $a=2p=2h$~\cite{kim-micro}. According to this configuration, the total number of groups, denoted as $g$ in the dragonfly network would be $g = a*h+1 $, the total number of compute nodes denoted as $N$ in the network would be $N = p*a*g $. An example dragonfly network is illustrated in Figure~\ref{fig:dragonfly-overview}. There are six routers in each group $(a=6)$, three compute nodes per router $(p=3)$, and three global channels per router $(h=3)$. This dragonfly network consists of 19 groups and 342 nodes in total.

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.48\textwidth]{dragonfly-overview}
  \caption{Five group slice of a 19-group dragonfly network. Job $J1$ is allocated using random placement, while Job $J2$ is allocated using contiguous placement.}
  \label{fig:dragonfly-overview}
\end{figure}

\textbf{Minimal:} In this policy, a message takes the minimal (shortest) path from the source router to the destination router. When there are multiple minimal paths between the source and destination, the message will be evenly divided among the paths. Minimal routing can guarantee the minimum hops the message takes from the source to the destination. However, it may result in congestion along the minimal paths.

\textbf{Adaptive:} In this policy, the path a message takes will be adaptively chosen between minimal and non-minimal paths, depending on the congestion situation along those paths. For the non-minimal path, an intermediate router in a separate group will be randomly chosen. The message takes the intermediate router as a via point, connecting the source and destination router through two separate minimal paths. Adaptive routing can avoid hot-spots in the presence of congestion and collapse to minimal routing otherwise.

\textbf{Progressive Adaptive:} In this policy, the decision to route minimally at each hop in the source group will be re-evaluated \TODO{packet granularity? flit granularity?}. Any decision to route non-minimally at source router or at a subsequent hop is permanent and will not be re-evaluated~\cite{jiang} \TODO{I thought PA does do re-evaluation?}. Progressive adaptive routing is capable of handling the case when a global channel is congested but the source router has not been informed yet~\cite{jiang}. The packet will take the non-minimal route only when the congestion is encountered.

@@
